Molecular dynamics simulation of synchronization in driven particles

### 2021-01-29 manuscript/manuscript_ajp_2020.tex
updated some brownian text

\begin{table}[h!]
\centering
\caption{Simulation parameters and units and comparable
  experimental values~\cite{Juniper2015}.
  Blanks %in the experimental parameters
  indicate
  units, rather than parameters that
  are not easily represented by a single value.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental value\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
temperature & $T_0 = 0$ \footnote{see Ex.~\ref{ex:brownian} to include temperature in the limit where $U_0 \sim k_B T$.} & $T \sim 300K $ \\

@@

  % (a) 
  In simulation we define our temperature parameter
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  This allows us to choose
e  a temperature that is easily compared to
  the other system parameters that scale the forces.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  motion along the $y-$direction, 
  measure the position vs. time
  of a non-driven colloid for $T/A_p = 0.5, 1.0$, and $2.0$
  when Brownian motion is included
  in the model.
  Confirm that a particle will hop a barrier
  for sufficiently high $T/A_p$ ratios.

>>>>

\begin{table}[h!]
\centering
\caption{Simulation parameters and units and comparable
  experimental values~\cite{Juniper2015}.
  Blanks %in the experimental parameters
  indicate
  units, rather than parameters that
  are not easily represented by a single value.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental value\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
temperature & $T_0 = 0$ \footnote{to learn more about the effects
  of temperature on this simulation
  see Ex.~\ref{ex:brownian} where we study the limit
  $U_0 \sim k_B T$.} & $T \sim 300K $ \\

@@

  % (a) 
  In simulation we define our temperature parameter to
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  In these units we can compare 
  simulation temperature directly
  to force 
  in order to estimate the degree of random fluctuation.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  Measure the position vs. time
  of a non-driven colloid for $T/A_p = 2.0, 4.0, 6.0$
  and note  a particle will hop a barrier
  for sufficiently high $T/A_p$ ratios.
  We find the crossover
  to a hopping regime at $T/A_p \approx 5.6$
  %when
